### 2017-06-23 manuscript/usses_water_ms.Rmd
trivia and log regressions for fig 1

Here we report the results of a five-year precipitation manipulation experiment in a sagebrush steppe grassland.
We imposed drought and irrigation treatments (50\% decrease/increase) and measured ecosystem (ANPP) and community (species composition) responses.
We focus on how the drought and irrigation treatments affect the linear relationship between ANPP and growing season precipitation, and if community dynamics underly the ecosystem responses.
In particular, we sought to answer the following questions:

1. Does drought or irrigation impact mean ANPP (i.e., different intercepts)?
2. Does drought or irrigation impact the effect of ambient precipitation on ANPP (i.e., different slopes)?
3. Is the resistance or sensitivity of ANPP to altered precipitation related to underlying community dynamics?

>>>>

Here we report the results of a five-year precipitation manipulation experiment in a sagebrush steppe grassland.
We imposed drought and irrigation treatments (50\% decrease/increase) and measured ecosystem (ANPP) and community (species composition) responses.
We focus on how the drought and irrigation treatments affect the linear relationship between ANPP and available soil moisture, and if community dynamics underly the ecosystem responses.
In particular, we are interested in the consistency of the ANPP-soil moisture relationship among treatments.
Is the relationship steeper under the drought treatment, at low soil moisture?
Does the relationship saturate under the irrigation treatment, at high soil moisture?
To answer these questions we fit a random intercepts, random slopes model to test whether the regressions differed among treatments.
